Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-04-14 doc/manuscript_hkk_drought_sensitivity.Rmd
updated table

ft <- flextable(sumtab)
ft <- set_header_labels(ft,
  na = ""
)
ft <- hline(ft, i = c(1, 7, 10), part = "body")
ft <- line_spacing(ft, space = 1, part = "all")
ft <- autofit(ft)
# ft <- height(ft, height = 0.3)
ft <- bold(ft, i = c(1, 7, 10), bold = TRUE, part = "body")
ft <- width(ft, 1, width = 3.5)
# ft <- width(ft, 2, width = 1.75)
# ft <- width(ft, 3, width = 3)
ft <- set_caption(ft, caption = "Summary table of hypotheses tested, effects of variables on drought sensitivity and corresponding evidence. For each variable x year combination, \"+\" indicates a positive effect, \"-\" indicates a negative effect and \"n.s.\" indicates that the effect was not statistically significant.")
ft
```

>>>>

ft <- flextable(sumtab)
ft <- set_header_labels(ft,
  na = ""
)
ft <- hline(ft, i = c(1, 4, 7), part = "body")
ft <- line_spacing(ft, space = 1, part = "all")
ft <- autofit(ft)
# ft <- height(ft, height = 0.3)
ft <- bold(ft, i = c(1, 4, 7), bold = TRUE, part = "body")
ft <- width(ft, 1, width = 3.5)
# ft <- width(ft, 2, width = 1.75)
# ft <- width(ft, 3, width = 3)
ft <- set_caption(ft, caption = "Summary table of hypotheses tested, effects of variables on drought sensitivity and corresponding evidence. For each variable x year combination, \"+\" indicates a positive effect, \"-\" indicates a negative effect and \"n.s.\" indicates that the effect was not statistically significant.")
ft
```
